Quality Definitions of Qualities

### 2019-10-22 StateOfPractice/QDefOfQualities/QDefOfQualities.tex
added definitions for correctness and installability

\title{Quality Definitions of Qualities} 
\author{Spencer Smith}{McMaster University, Canada}{smiths@mcmaster.ca}{}{}
\author{Jacques Carette}{McMaster University, Canada}{carette@mcmaster.ca}{}{}
\author{Olu Owojaiye}{McMaster University, Canada}{}{}{}
\author{Peter Michalski}{McMaster University, Canada}{}{}{}
\author{Ao Dong}{McMaster University, Canada}{}{}{}

@@

\subsection{Installability}

A measure of the ease of installation.\\
Installability is related to the effort required to install a software in a specified environment. In other words, its capability to be installed in a specified environment.

\subsection{Correctness}

Software is correct if it matches its specification.  There is no direct tool or
method for measuring correctness. One way of building confidence in correctness
is by reviewing to ensure that each requirement stated is one that the
stakeholders and experts desire.  By maintaining traceability, consistency and
unambiguity, we can reduce the occurrence of errors and make the goal of
reviewing for correctness easier.\\
 The extent to which a software's specification, design and implementation is free from errors is its correctness. The quality of a software's operation is dependent on the degree of correctness \cite{berander2005software}. Correctness and reliability are said to have dependencies, such that if a system exhibits a high degree of correctness then it tends to be reliable.

>>>>

\title{Quality Definitions of Qualities} 
\author{Spencer Smith}{McMaster University, Canada}{smiths@mcmaster.ca}{}{}
\author{Jacques Carette}{McMaster University, Canada}{carette@mcmaster.ca}{}{}
\author{Olu Owojaiye}{McMaster University, Canada}{owojaiyo@mcmaster.ca}{}{}
\author{Peter Michalski}{McMaster University, Canada}{}{}{}
\author{Ao Dong}{McMaster University, Canada}{}{}{}

@@

\subsection{Installability}
\begin{itemize}
    \item{Definition 1:} A measure of the ease of installation.\\
	\item{Definition 2:} Installability is related to the amount of human effort required to install a software in a designated environment \cite{berander2005software}. \\
	\item{Definition 3:} ``The capability of a software product to be installed in a specified environment'' \cite{berander2005software}.\\
	\item{Definition 4:}  ``The efficacy of the installation, uninstallation or reinstallation process of a software product in a specified enviroment'' (\cite{iso201017043})\\
	\item {\textbf{Proposed definition}:} (Definition 2)
\end{itemize}

\subsection{Correctness}
\begin{itemize}
	\item{Definition 1:} The degree to which a software's specification is satisfied (\cite{berander2005software}).\\
	\item{Definition 2:} A software is correct if it functions according to its specified functional and non-functional specification(\cite{GhezziEtAl2003})\\.
	\item{Definition 3:} According to \cite{wilson2009quality}, ``the degree to which a system is free from defects in its specification, design, and implementation, is its correctness.\\
	\item{Definition 4:} ``The ability of software products to perform their exact tasks, as defined by their specification'' (\cite{meyer1988object}). \\
	\item{\textbf{Proposed definition}:} Definition 2
\end{itemize}

\subsubsection{Discussion}
There is no direct tool or
method for measuring correctness. One way of building confidence in correctness
is by reviewing to ensure that each requirement stated is one that the
stakeholders and experts desire.  By maintaining traceability, consistency and
unambiguity, we can reduce the occurrence of errors and make the goal of
reviewing for correctness easier.\\
 The quality of a software's operation is dependent on the degree of correctness \cite{berander2005software}. Correctness and reliability are said to have dependencies, such that if a system exhibits a high degree of correctness then it tends to be reliable (\cite{GhezziEtAl2003}).
